### 2021-08-26 A methodological framework to enable the roaming agreement digitalization: An NLP-based approach/paper.tex
26.08.21.6

\begin{document}
\title{A methodological framework to enable the roaming agreement digitization: An NLP-based approach\\}

@@

However, a successful RA drafting goes through a complex negotiation process in which, currently the parties, i.e. the Mobile Network Operators (MNOs), still use asynchronous flows such as email or even regular mail for information exchange. Since these processes lack transparency, which can result in the violation of the RA by MNOs, it is necessary to provide a transparent digitization system for RA drafting negotiations. For this reason, this paper proposes the use of Natural Language Processing (NLP) as an engine to digitize the legal text as a starting point of a RA transparent drafting process. The NLP engine analyzes the different articles and sub-articles of the RA determining the existence of variables, variations, standard clauses and customized texts in the text. For this purpose, on the one hand, NLP techniques such as Named Entity Recognition (NER) and Part of Speech (POS) are applied from an unstructured data information discovery tools such as \textit{Amazon Comprehend} and on the other hand, a comprehensive comparison between texts is established based on \textit{similarity} determination techniques. Both techniques are integrated as part of the development of an unstructured text processing tool that integrates an specific methodology for the use case, i.e., a transparent digitization of roaming agreements.

The rest of this manuscript is structured as follows: Section 2 reviews both attempts at a transparent digitization of Roaming Agreement and existing NLP-based digitization mechanisms as part of the related work. Section 3 establishes the designed methodology. The implementation of our system are described in Section 4. Section 6 discusses the results of conducted experiments. Finally, the conclusions of the manuscript are included in Section 7.

@@

Both in the scientific literature and in business environments there are important approaches to RA digitization. Thus, the reference \cite{9369516} proposes a dynamic RA between the Local 5G Operator and the MNO. The interaction between the two entities takes place through an Ethereum based platform. A second approach focuses uniquely on the billing of the services obtained as a result of the RA \cite{9024541}. This agreement is incorporated as part of a smart contract so the work contributes significantly to the digitization process of the agreement, allowing for a faster, more seamless process in which payments can be requested and obtained quickly due to less need for manual intervention. The contextualization of this system in the business environment is proposed by important MNOs such as Telefonica, Deutsche Telekom and Vodafone which use blockchain for Roaming settlement within the framework of the RA between the parties \cite{Huillet2020}. However, these contributions are focused from a RA technical perspective rather than the context of a transparent digitization to enhance the negotiation process for the effective drafting of the roaming agreement.

Additionally, the scientific literature addresses text processing systems based on nlp techniques in domains such as judiciary. Thus, the reference \cite{8487847} addresses the process of digitization in the judicial sectors from archives of court records for which the authors have designed a textual analysis tool that includes grammatical analysis of documents in English based on NLP techniques. This linguistic analysis attempts to find the appropriate meaning of terms within a document. In addition, the reference \cite{9138070} applies NLP-based processing techniques for information retrieval from spreadsheets and describes technologies for storing and retrieving database information. NLP techniques such as sentence tokenization, word tokenization, removing stopwords and lemmatization are part of the parsing stage of the work. Finally, authors of reference \cite{9104105} propose a model for implementing sentimental analysis using Amazon Comprehend. This system performs an audio-to-text transcription and then performs the processing of the obtained text. Although these studies  constitute a relevant part of related work, e.g., by integrating useful tools such as Amazon Comprehend or detailing the use of techniques such as tokenization, the scientific literature does not address scenarios for the telecom field and even less in the context of a transparent digitization of the roaming agreement. Therefore, we can affirm that our work introduces a topic with a high degree of novelty.

@@

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.25\textwidth]{images/NLP_Engine.png}}
\caption{NLP Engine overall architecture.}
\label{fig1}
\end{figure}

@@

\subsection{Accuracy determination based on symbol comparison}
The second accuracy analysis involves establishing a comparison between the sub-articles populated in the output file with respect to the sub-articles existing in the input file containing the Roaming Agreements. For that purpose, the text comparison tool [Countwordsfree](https://countwordsfree.comcomparetexts) has been used manually copying sub-article by sub-article. For each sub-article is determined:
 \begin{enumerate}
\item Common percentage of words between compared sub-articles.
\item Difference percentage of words between compared sub-articles.
\item Common words between compared sub-articles.
\item Difference words between compared sub-articles.
\end{enumerate}

@@

\section{Conclusions}
Define abbreviations and acronyms the first time they are used in the text

>>>>

\begin{document}
\title{A methodological framework to enable the roaming agreement digitalization: An NLP-based approach\\}

@@

However, a successful RA drafting goes through a complex negotiation process in which, currently the parties, i.e. the Mobile Network Operators (MNOs), still use asynchronous flows such as email or even regular mail for information exchange. Since these processes lack transparency, which can result in the violation of the RA by MNOs, it is necessary to provide a transparent digitalization system for RA drafting negotiations. For this reason, this paper proposes the use of Natural Language Processing (NLP) as an engine to digitize the legal text as a starting point of a RA transparent drafting process. The NLP engine analyzes the different articles and sub-articles of the RA determining the existence of variables, variations, standard clauses and customized texts in the text. For this purpose, on the one hand, NLP techniques such as Named Entity Recognition (NER) and Part of Speech (POS) are applied from an unstructured data information discovery tools such as \textit{Amazon Comprehend} and on the other hand, a comprehensive comparison between texts is established based on \textit{similarity} determination techniques. Both techniques are integrated as part of the development of an unstructured text processing tool that integrates an specific methodology for the use case, i.e., a transparent digitalization of roaming agreements.

The rest of this manuscript is structured as follows: Section 2 reviews both attempts at a transparent digitalization of Roaming Agreement and existing NLP-based digitalization mechanisms as part of the related work. Section 3 establishes the designed methodology. The implementation of our system are described in Section 4. Section 6 discusses the results of conducted experiments. Finally, the conclusions of the manuscript are included in Section 7.

@@

Both in the scientific literature and in business environments there are important approaches to RA digitalization. Thus, the reference \cite{9369516} proposes a dynamic RA between the Local 5G Operator and the MNO. The interaction between the two entities takes place through an Ethereum based platform. A second approach focuses uniquely on the billing of the services obtained as a result of the RA \cite{9024541}. This agreement is incorporated as part of a smart contract so the work contributes significantly to the digitalization process of the agreement, allowing for a faster, more seamless process in which payments can be requested and obtained quickly due to less need for manual intervention. The contextualization of this system in the business environment is proposed by important MNOs such as Telefonica, Deutsche Telekom and Vodafone which use blockchain for Roaming settlement within the framework of the RA between the parties \cite{Huillet2020}. However, these contributions are focused from a RA technical perspective rather than the context of a transparent digitization to enhance the negotiation process for the effective drafting of the roaming agreement.

Additionally, the scientific literature addresses text processing systems based on nlp techniques in domains such as judiciary. Thus, the reference \cite{8487847} addresses the process of digitalization in the judicial sectors from archives of court records for which the authors have designed a textual analysis tool that includes grammatical analysis of documents in English based on NLP techniques. This linguistic analysis attempts to find the appropriate meaning of terms within a document. In addition, the reference \cite{9138070} applies NLP-based processing techniques for information retrieval from spreadsheets and describes technologies for storing and retrieving database information. NLP techniques such as sentence tokenization, word tokenization, removing stopwords and lemmatization are part of the parsing stage of the work. Finally, authors of reference \cite{9104105} propose a model for implementing sentimental analysis using Amazon Comprehend. This system performs an audio-to-text transcription and then performs the processing of the obtained text. Although these studies  constitute a relevant part of related work, e.g., by integrating useful tools such as Amazon Comprehend or detailing the use of techniques such as tokenization, the scientific literature does not address scenarios for the telecom field and even less in the context of a transparent digitalization of the roaming agreement. Therefore, we can affirm that our work introduces a topic with a high degree of novelty.

@@

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.2\textwidth]{images/NLP_Engine.png}}
\caption{NLP Engine overall architecture.}
\label{fig1}
\end{figure}

@@

\subsection{Accuracy determination based on symbol comparison}
The second accuracy analysis involves establishing a comparison between the sub-articles populated in the output file with respect to the sub-articles existing in the input file containing the Roaming Agreements. For that purpose, the text comparison tool Countwordsfree(\cite{countwordsfree}) has been used manually copying sub-article by sub-article. For each sub-article is determined:
 \begin{enumerate}
\item Common percentage of words between compared sub-articles.
\item Difference percentage of words between compared sub-articles.
\item Common words between compared sub-articles.
\item Difference words between compared sub-articles.
\end{enumerate}

@@

\section{Conclusions}
Considering that the proposed NLP Engine constitutes a part of a project that has as main objective of transforming the current Telecommunication Roaming Agreement drafting and negotiation process into a digitalized version based on the transparency promoted by blockchain technology, future research works include the design, development and evaluation of the rest of the sub-systems, as well as the integration of the NLP Engine part.
